CommonMind Consortium: DLPFC

### 2020-09-23 combined_analysis/diff.networks.Rmd
Update diff networks

rmarkdown::render("combined_analysis/diff.networks.Rmd")

@@

df_test = lapply( 1:10, function(k){
	METADATA$rnd = sample(c('A','B'), nrow(METADATA), replace=TRUE)
	METADATA$rnd = factor(METADATA$rnd, c('A','B'))

>>>>

rmarkdown::render("combined_analysis/diff.networks.Rmd", output_dir="/sc/arion/scratch/hoffmg01/network")

@@

df_test = lapply( 1, function(k){
	METADATA$rnd = sample(c('A','B'), nrow(METADATA), replace=TRUE)
	METADATA$rnd = factor(METADATA$rnd, c('A','B'))
